Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-02 PandaEvolution.tex
Address Jack's comment issue #9

Titan’s backfill functionality offers the opportunity to avoid the overhead of
queue wait times without using pilot abstraction. Backfill availability is the
number of node-hours (or core-hours) that  is not utilized by regular jobs
submitted to the queues on Titan. Titan’s backfill functionality offers the
opportunity to avoid the overhead of queue wait times without using pilot
abstraction.  It is important to note that backfill availability is  computed
retrospectively and is determined by Titan's operation team. Backfill
availability represents the theoretical maximum of node-hours that could be
utilized by ATLAS (or any other project) that submit under backfill mode.

Compared to pilots, backfill has the disadvantage of limiting the amount of
work nodes that can be requested. Pilots are normal jobs: they can request as
many worker nodes for as much time as a queue can offer. On the contrary, jobs
sized on the basis of backfill information availability depend on the number
of worker nodes that cannot be given to any other job in the Titan's queue. %
\sergeynote{any other job currently in the Titan's queue?}\mtnote{Better?}.

>>>>

Titan’s backfill functionality offers the opportunity to avoid the overhead of
queue wait times without using pilot abstraction~\cite{maui_backfill_url}.
Backfill availability is the number of node-hours (or core-hours) that cannot be
utilized by regular jobs queued on Titan at a specific point in time.  It is
important to note that backfill availability is computed retrospectively and is
determined by Titan's operation team. Backfill availability represents the
theoretical maximum of node-hours that could be utilized by ATLAS (or any other
project) that submit under backfill mode.

Compared to pilots, backfill has the disadvantage of limiting the amount of work
nodes that can be requested. Pilots are normal jobs: they can request as many
worker nodes for as much time as a queue can offer. On the contrary, jobs sized
on the basis of backfill information availability depend on the number of worker
nodes that cannot be given to any other job in the Titan's queue at that moment
in time.

% \sergeynote{any other job currently in the Titan's queue?}\mtnote{Better?}.
